---
title: "USD MXN"
author: "Pablo Rodriguez Chavez"
date: "April 29, 2018"
output: html_document
---


# Introduction

This is a simple test of the functionality offered by the plotly library.
We will compare the plots offered by plain vanilla plotly against the ggplot2 ones with added plotly functionality

The data was downloades from St. Louis Fed website : https://fred.stlouisfed.org/series/DEXMXUS

```{r, echo=TRUE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(plotly)
library(lubridate)
```

Load the data, and a little preprocessing.

```{r, echo=TRUE}
setwd("C:/Users/Pablo/Dropbox/DataProducts/week3")
prices<-read.csv("DEXMXUS.csv", header=TRUE,stringsAsFactors = FALSE)

prices<-prices[complete.cases(prices),]
prices$DATE<-ymd(prices$DATE)
prices$DEXMXUS<-as.numeric(prices$DEXMXUS)
prices<-prices[complete.cases(prices),]

```
## Plotly
```{r, echo=TRUE}
p1<-plot_ly(data=prices, x=~DATE,y=~DEXMXUS,type="scatter",mode="lines")
p1

```

## ggplot Plain Vanilla  
```{r, echo=TRUE, cache=TRUE}
p2<-ggplot(data=prices)+geom_line(aes(x=DATE,y=DEXMXUS))
p2
```

## ggplotly: Plotly renderin ggplot object
```{r, echo=TRUE}
p3<-ggplotly(p2)
p3
```